---
title: "Overview of courseraRPackageProj"
author: "Joao Teixeira"
date: "`2018-08-20`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of courseraRPackageProj}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
knitr::opts_knit$set(root.dir = normalizePath("../inst/extdata"))
library(courseraRPackageProj)
```

The CourseraRPackageProj Package provides functions for summarizing and plotting data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. 

## Reading data

The `make_filename` function creates the filename for the year provided, while the `fars_read` function will read in the file associated to the filename. 

```{r, fig.show='hold'}
filename <- make_filename(2013)
data <- fars_read(filename)
head(data)
```

## Summarise Data

The `fars_read_years` function returns a list of tibbles for each year provided, with two columns, year and month.

```{r, echo=TRUE, results='asis'}
years <- c(2014, 2015)
dat <- fars_read_years(years)
knitr::kable(head(dat[[1]]))
```

The `fars_summarize_years` summarizes the counts of incidents for each month in the years provided.

```{r, echo=TRUE, results='asis'}
years <- c(2014, 2015)
dat_sum <- fars_summarize_years(years)
knitr::kable(head(dat_sum))
```

## Plot Data

The `fars_map_state` function returns a map with the cases in a given year plotted over their state.

```{r, echo=TRUE, results='asis'}
fars_map_state(6, 2014)
